Multisensor Architecture for an Intersection Management System

### 2019-01-22 ch3-arch_sys.tex
Added TODOs
Reviewed processing stages and detailed simulation models

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situations or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, including a list of common tasks performed at each of these stages and also it is shown how the data volume is reduced while data meaning increases in the last stages.

@@

Three widely-known models for this kind of analysis are macroscopic model, microscopic model and mesoscopic model. The macroscopic model of traffic flow is based on a hydrodynamic analogy, modeling traffic as a fluid process characterized by three main variables, density, volume and speed, and the objective is to describe time-space evolution of those variables.

@@

>>>>

In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene. Spatial-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situations or events of interest. This output could be delivered to an automated or semi-automated stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, including a list of common tasks performed at each of these stages.

@@

Three widely-known models for this kind of analysis are macroscopic model, microscopic model and mesoscopic model. The macroscopic model of traffic flow is based on a hydrodynamic analogy, modeling traffic as a fluid process characterized by three main variables, density, volume and speed, and the objective is to describe time-space evolution of those variables. The microscopic model aims to detail at a high detail inter-vehicles interactions and their individual state. For example, in a lane-change maneuver the state of the car doing the action and those affected by it, is individually tracked. The mesoscopic model tries to include features of both macroscopic and mesoscopic model. In this case, the same lane-change maneuver could be seen as an instant action triggered by lane density rather than on individual interactions.

@@

\todo{Design Considerations}
